---
title: "Assigment5"
author: "Griffin J. Lane"
date: "October 10, 2017"
output: html_document
---
##1. ###a. Import the .txt file into R
```{r}
df <- read.csv2("C:/Users/Griff/OneDrive/Documents/!_SKOOL/Doing Data Science/Datasets/yob2016.txt", sep = ";") #read.csv2 can handle .txt extensions
names(df) <- c("Name", "Sex", "NameCount")
```
###b. Display the summary and structure of df
```{r}
summary(df)
str(df)
```
###c. Write an R command to figure out which name is repeated and display it
```{r}
mistake <- grep('[yY]{3}$', df$Name, value = TRUE)
```
###d. Please remove this particular observation
```{r}
df<- df[df$Name != mistake,,]
```

##2. ###a. Import the .txt file into R
```{r}
df2 <- read.csv2("C:/Users/Griff/OneDrive/Documents/!_SKOOL/Doing Data Science/Datasets/yob2015.txt", sep = ",") 
names(df2) <- c("Name","Sex", "NameCount")
```
###b. Display the last ten rows in the dataframe. Describe.
```{r}
tail(df2,10)
##All of the names listed are males with 5 occurrences of their name
```
###c. Merge y2016 and y2015 by your Name column; assign it to final
```{r}
final <- merge(df,df2, by = "Name", na.rm = TRUE)
```

##3. ###a. Create a new column called “Total” in final that adds the amount of children in 2015 and 2016 together.
```{r}
final$Total <- final$NameCount.x+final$NameCount.y
```
###.b Sort the data by Total and report the top ten names
```{r}
final <- final[order(final$Total, decreasing = TRUE),]
names(final) <-  c("Name", "Sex2015","NameCount2015","Sex2016","NameCount2016","Total")
head(final,10)
```
###c. Omit boys and give the top 10 most popular girl’s names
```{r}
girls <- final[final$Sex2015=="F" & final$Sex2016 == "F",]
girls <- data.frame(Names=girls$Name,Total=girls$Total)
head(girls,10)

##writing to file
write.csv(head(girls,10), "TopGirlNames2015-2016.csv")
```